Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2019-01-28 paper/paper.tex
updated authors superscript, this is the version to be submitted.

\author{
	\firstname{Ren\'e} \lastname{Caspart}\inst{1}\fnsep\thanks{\email{rene.caspart@cern.ch}} \and
	\firstname{Patrick} \lastname{Firnkes}\inst{2}\fnsep\thanks{\email{patrick.firnkes@student.kit.edu}} \and
	\firstname{Manuel} \lastname{Giffels}\inst{1}\fnsep\thanks{\email{manuel.giffels@cern.ch}} \and
	\firstname{Anne} \lastname{Koziolek}\inst{2}\fnsep\thanks{\email{koziolek@kit.edu}} \and
	\firstname{G\"unter} \lastname{Quast}\inst{1}\fnsep\thanks{\email{g.quast@kit.edu}} \and
	\firstname{Ralf} \lastname{Reussner}\inst{2}\fnsep\thanks{\email{reussner@kit.edu}} \and
	\firstname{Maximilian} \lastname{Stemmer-Grabow}\inst{2}\fnsep\thanks{\email{mail@mxsg.de}}
}

>>>>

\author{
	\firstname{Ren\'e} \lastname{Caspart}\inst{1}\thanks{\email{rene.caspart@cern.ch}} \and
	\firstname{Patrick} \lastname{Firnkes}\inst{2}\thanks{\email{patrick.firnkes@student.kit.edu}} \and
	\firstname{Manuel} \lastname{Giffels}\inst{1}\thanks{\email{manuel.giffels@cern.ch}} \and
	\firstname{Anne} \lastname{Koziolek}\inst{2}\thanks{\email{koziolek@kit.edu}} \and
	\firstname{G\"unter} \lastname{Quast}\inst{1}\thanks{\email{g.quast@kit.edu}} \and
	\firstname{Ralf} \lastname{Reussner}\inst{2}\thanks{\email{reussner@kit.edu}} \and
	\firstname{Maximilian} \lastname{Stemmer-Grabow}\inst{2}\thanks{\email{mail@mxsg.de}}
}
